\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-03-24 papers/jss/article.Rnw
Replace sweave code with manual CodeInput/CodeOutput for now so this is buildable again with protobuf-2.5 library which doesn't like our unittest.proto.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@880 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<echo=FALSE,print=FALSE>>=
if (!exists("protobuf_unittest.TestAllTypes",
            "RProtoBuf:DescriptorPool")) {
    unittest.proto.file <- system.file("unitTests", "data",
                                       "unittest.proto",
                                       package="RProtoBuf")
    readProtoFiles(file=unittest.proto.file)
}
@

@@

<<>>=
test <- new(protobuf_unittest.TestAllTypes)
test$repeated_int64 <- c(2^53, 2^53+1)
length(unique(test$repeated_int64))
@

@@

<<>>=
test$repeated_int64 <- c("9007199254740992", "9007199254740993")
@

@@

<<>>=
options("RProtoBuf.int64AsString" = FALSE)
test$repeated_int64
length(unique(test$repeated_int64))
options("RProtoBuf.int64AsString" = TRUE)
test$repeated_int64
length(unique(test$repeated_int64))
@

>>>>

<<echo=FALSE,print=FALSE,eval=FALSE>>=
if (!exists("protobuf_unittest.TestAllTypes",
            "RProtoBuf:DescriptorPool")) {
    unittest.proto.file <- system.file("unitTests", "data",
                                       "unittest.proto",
                                       package="RProtoBuf")
    readProtoFiles(file=unittest.proto.file)
}
@

@@

% We want a cleaner error message here.
\begin{CodeChunk}
\begin{CodeInput}
R> test <- new(protobuf_unittest.TestAllTypes)
R> test$repeated_int64 <- c(2^53, 2^53+1)
R> length(unique(test$repeated_int64))
\end{CodeInput}
\begin{CodeOutput}
[1] 1
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> test$repeated_int64 <- c("9007199254740992", "9007199254740993")
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> options("RProtoBuf.int64AsString" = FALSE)
R> test$repeated_int64
\end{CodeInput}
\begin{CodeOutput}
[1] 9.007e+15 9.007e+15
\end{CodeOutput}
\begin{CodeInput}
R> length(unique(test$repeated_int64))
\end{CodeInput}
\begin{CodeOutput}
[1] 1
\end{CodeOutput}
\begin{CodeInput}
R> options("RProtoBuf.int64AsString" = TRUE)
R> test$repeated_int64
\end{CodeInput}
\begin{CodeOutput}
[1] "9007199254740992" "9007199254740993"
\end{CodeOutput}
\begin{CodeInput}
R> length(unique(test$repeated_int64))
\end{CodeInput}
\begin{CodeOutput}
[1] 2
\end{CodeOutput}
\end{CodeChunk}
